---
title: "Introduction to Strategy Games"
author: "Brian Gilbert, Linde Chen, Olivia Iles, Anna Xu"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to strategygames}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
The strategygames packages introduces 4 simple strategy games to users of R:

* Chinese Poker
* Boggle
* Tic Tac Toe
* Black Jack 

This document introduces you to strategygame's basic functions and how to use them in the games.

## **Chinese Poker**

chinese.poker() allows you to begin playing a game of Chinese Poker with two computer opponents. Once this function is run and the game begins, the user will be dealt a hand of 18 cards as such. 

These 18 cards will be automatically sorted for the user for ease of viewing. At each turn, the user will be prompted as to whether or not he/she would like to check his/her current hand. 

## **Boggle**

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
