---
title: "Introduction to Strategy Games"
author: "Brian Gilbert, Linde Chen, Olivia Iles, Anna Xu"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to strategygames}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
The strategygames packages introduces 4 simple strategy games to users of R:

* Chinese Poker
* Boggle
* Tic Tac Toe
* Black Jack 

This document introduces you to strategygame's basic functions and how to use them in the games.

## **Chinese Poker**

chinese.poker() allows you to begin playing a game of Chinese Poker with two computer opponents. Once this function is run and the game begins, the user will be dealt a hand of 18 cards as such. 

These 18 cards will be automatically sorted for the user for ease of viewing. At each turn, the user will be prompted as to whether or not he/she would like to check his/her current hand. 

## **Boggle**

Calling boggle_play allows the user to play an adapted version of Boggle. The user must enter words that are able to be made by combining adjacent letters on the board. The program keeps track of the words entered, and it can display all possible words if requested. The program gives instructions for its use.
The game differs from standard boggle in the following ways. First, the same letter square may be used twice in the same word, as long as it is not used consecutively. Also, the Boggle program uses a considerably reduced dictionary. The list of word comes from the list of 10000 most common English words as compiled in the following GitHub repo: https://github.com/first20hours/google-10000-english. This list was further cut down by considering only words of 3-6 letters. This list was compiled from Google data, so it contains some words that are not Standard English (such as "lol"), and it does not contain many words that are familiar to the average user yet fall outside the top 10000 common words.

## **Tic Tac Toe**

Calling the function ticTacToe() lets users play a game of Tic Tac Toe against the computer. The gameboard is displayed in the R plot window, and users click on board squares to make their move. The game ends when one player gets three of their pieces in a row, or no more moves can be made (a draw). The clearBoard() function can be called after a game to reset the board.

## **Black Jack**

blackjack() allows you to play Black Jack in the R command window. The user first indicates whether they want a hand or if they want to input their own hand. Since Black Jack only depends on the value of each card, the user will receive the values of their card (2-10, where 10 can be either from the card 10, King, or Queen). If the user receives an Ace, this will be indicated by the card 13, and they will be asked to then set a binding value for Ace. They are then asked if they'd like to continue drawing. When they stop drawing, it will then be player 2's (i.e., the computer/dealer) turn. Once the game ends, they are shown the sum of both players. They can then replay. Once they decide to no longer replay, the user will be shown their score and the computer's score. 

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
